Pure Spin Current Injection in Hydrogenated Graphene Structures

### 2017-04-05 mu/article/article.tex
Alt responses almost finished.

% \documentclass[]{article}
\documentclass[twocolumn]{article}

\usepackage{geometry}
\geometry{letterpaper, margin=2cm}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{cuted}
\usepackage{blindtext}
\usepackage{color}
\usepackage[inline]{showlabels}
\usepackage{showframe}

\usepackage[section]{placeins}
\let\Oldsection\section
\renewcommand{\section}{\FloatBarrier\Oldsection}
\let\Oldsubsection\subsection
\renewcommand{\subsection}{\FloatBarrier\Oldsubsection}
\let\Oldsubsubsection\subsubsection
\renewcommand{\subsubsection}{\FloatBarrier\Oldsubsubsection}

\title{Pure Spin Current Injection in Hydrogenated Graphene Structures}
\author{Reinaldo Zapata-Pe\~na,
Bernardo S. Mendoza,
Anatoli I. Shkrebtii}
\date{}

\begin{document}
\maketitle

\section{abstract} % (fold)
\label{sec:abstract}
\textcolor{red}{{\huge Filling with text.}\\ \blindtext}
% section abstract (end)

\section{Introuction} % (fold)
\label{sec:introuction}

\textcolor{red}{\blindtext}
\begin{figure}[ht!]
    \centering
    \includegraphics[width=\linewidth]{figures/altstruc2}
    \includegraphics[width=\linewidth]{figures/altstruc1}
    \caption{Alt structure.}
    \label{fig:altstruc}
\end{figure}
\begin{figure}[ht!]
    \centering
    \includegraphics[width=\linewidth]{figures/upstruc2}
    \includegraphics[width=\linewidth]{figures/upstruc1}
    \caption{Up structure}
    \label{fig:upstruc}
\end{figure}
% \begin{figure}[tb]
%     \centering
%     \includegraphics[width=\linewidth]{figures/hnbGh-aa-1}
%     \includegraphics[width=\linewidth]{figures/hnbGh-aa-2}
%     \caption{HNBC$_{2}$H-aa structure}
%     \label{fig:aastruc}
% \end{figure}
% \begin{figure}[tb]
%     \centering
%     \includegraphics[width=\linewidth]{figures/hnbGh-ab-1}
%     \includegraphics[width=\linewidth]{figures/hnbGh-ab-2}
%     \caption{HNBC$_{2}$H-ab structure}
%     \label{fig:abstruc}
% \end{figure}

% % section introuction (end)
\textcolor{red}{
\blindtext
\blindtext
\blindtext
}

@@

\begin{strip}
\begin{align}
\mathcal{V}^{\mathrm{ab}} (\omega) 
&= \frac{\mu^{\mathrm{abxx}}(\omega)
E^{2}(\omega)\cos^{2}(\alpha) + 
\mu^{\mathrm{abyy}}(\omega)
E^{2}(\omega)\sin^{2}(\alpha) + 
2\mu^{\mathrm{abxy}}(\omega)
E^{2}(\omega)\cos(\alpha)\sin(\alpha)}
{\xi^{\mathrm{xx}}(\omega)
E^{2}(\omega)\cos^{2}(\alpha) + 
\xi^{\mathrm{yy}}(\omega)
E^{2}(\omega)\sin^{2}(\alpha)},
\nonumber \\
&= \frac{\mu^{\mathrm{abxx}}(\omega)\cos^{2}(\alpha) + 
\mu^{\mathrm{abyy}}(\omega)\sin^{2}(\alpha) + 
2\mu^{\mathrm{abxy}}(\omega)\cos(\alpha)\sin(\alpha)}
{\xi^{\mathrm{xx}}(\omega)\cos^{2}(\alpha) + 
\xi^{\mathrm{yy}}(\omega)\sin^{2}(\alpha)}.
\label{eq:vab}
\end{align}
\end{strip}

@@

We also define $|\mathcal{V}^{\mathrm{a}}|$ as 
\begin{equation}\label{eq:va-mag}
|\mathcal{V}^{\mathrm{a}}| = 
\sqrt {
(\mathcal{V}^{\mathrm{ax}})^{2} +
(\mathcal{V}^{\mathrm{ay}})^{2} +
(\mathcal{V}^{\mathrm{az}})^{2} 
},
\end{equation}
and the corresponding polar and azimuthal angles $\theta$ and $\varphi$ as
\begin{align}
\theta  =& \cos^{-1} \left(  \frac{\mathcal{V}^{\mathrm{az}}}
{|\mathcal{V}^{\mathrm{a}}|} \right),
& 0 \leq &\theta \leq \pi, 
\label{eq:polar-ang} \\
\varphi =& \tan^{-1} \left( \frac{\mathcal{V}^{\mathrm{ay}}}{\mathcal{V}^{\mathrm{ax}}} \right),
& 0 \leq &\varphi \leq 2\pi. \\ 
\label{eq:azimuthal-ang} 
\end{align}

@@

We preset the results for $\mathcal{V}^{\mathrm{ab}}$ for the
C$_{16}$H$_{8}$-alt and C$_{16}$H$_{8}$-up structures being both
noncentrosymmetric semi-infinite carbon systems with 50\% hydrogenation in
different arrangements. The \emph{alt} system has alternating hydrogen atoms on
the upper and bottom sides of the carbon sheet, while the \emph{up} system has H
only on the upper side. We take the hexagonal carbon lattice to be on the $xy$
plane for both structures, and the carbon-hydrogen bonds on the perpendicular
$xz$ plane, as depicted in Figs.
\ref{fig:altstruc} and \ref{fig:upstruc}.

@@

\begin{table}[tb]
\center
\begin{tabular}{ccccc}\\
\hline
Layer & Atom & \multicolumn{3}{c}{Position [\AA]} \\
\cline{3-5}
No. & type & $x$ & $y$ & $z$  \\
\hline
1 & H &  -0.61516 &  -1.42140 & \ 1.47237 \\
2 & C &  -0.61516 &  -1.73300 & \ 0.39631 \\
3 & C & \ 0.61516 & \ 1.73300 & \ 0.15807 \\
4 & C & \ 0.61516 & \ 0.42201 &  -0.15814 \\
5 & C &  -0.61516 &  -0.37396 &  -0.39632 \\
6 & H &  -0.61516 &  -0.68566 &  -1.47237 \\
\hline
% \multicolumn{5}{c}{\includegraphics[width=0.4\linewidth]{figures/alt-unitcell-layers.pdf}} \\
% \hline
\end{tabular}
\caption{Unit cell of \emph{alt} structure. Layer division, atom types and
positions for the \emph{alt} structure. The structure unit cell was divided in
six layers corresponding each one to atoms in different $z$ positions. The
corresponding layer atom position is depicted in Fig. \ref{fig:altstruc} with
the corresponding number of layer.}
\label{tab:alt-unitcell}
\end{table}

The structures presented here where divided into layers to analyze the he layer-
by-layer contribution for $\mathcal{V}^{\mathrm{ab}}$ response. The \emph{alt}
structure was divided in six layers corresponding the first one to the top
hydrogen atoms, from the second to the forth to carbon atoms in different $z$
positions, and the sixth and last one to the bottom hydrogen atoms. The
\emph{up} structure was divided into two layers, the first one comprised by the
top hydrogen atoms and the second by the carbon atoms. The layer divisions and
atom positions for the unit cells are shown in Tables \ref{tab:alt-unitcell} and
\ref{tab:up-unitcell}.

\begin{table}[tb]
\center
\begin{tabular}{ccccc}\\
\hline
Layer & Atom & \multicolumn{3}{c}{Position [\AA]} \\
\cline{3-5}
No. & type & $x$ & $y$ & $z$  \\
\hline
1 & H & -0.61516 & -1.77416 &  0.73196 \\
1 & H &  0.61518 &  0.35514 &  0.73175 \\
2 & C & -0.61516 & -1.77264 & -0.49138 \\
2 & C & -0.61516 & -0.35600 & -0.72316 \\
2 & C &  0.61516 &  0.35763 & -0.49087 \\
\hline
\end{tabular}
\caption{Unit cell of \emph{up} structure. Layer division, atom types and
positions for the \emph{up} structure. The structure unit cell was divided in
two layers corresponding to hydrogen and carbon atoms.The corresponding layer
atom position is depicted in Fig. \ref{fig:upstruc} with the corresponding
number of layer.}
\label{tab:up-unitcell}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% ALT %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{alt} % (fold)
\label{sec:results-alt}

For the \emph{alt} structure we analized the energby range from 0.6\,eV to
1.0\,eV where we found the major response for $\mathcal{V}^{\mathrm{ab}}$ and
$|\mathcal{V}^{\mathrm{a}}|$. In Fig. \ref{fig:alt-magvxbincang} we present the
$|\mathcal{V}^{\mathrm{x}}|$ spectra resulting from evaluate Eq.
\eqref{eq:va-mag} using different polarization angles $\alpha$ in Eq.
\eqref{eq:vab} forthe C$_{16}$H$_{8}$-alt structure. The onset of the response
is when the energy of the incoming light is the same of the gap energy. From
this picture we can see that for the zone between the energy range of
0.90\,eV-0.93\,eV and polarization angles between 120$^{\circ}$ and
150$^{\circ}$ is the zone of the maximum response is held reaching
$|\mathcal{V}^{\mathrm{x}}|$ values of near to 30\,Km/s. Also there is a second
zone between the energy range of 0.70\,eV-0.74\,eV and same polarization angles
where a local maximum of $\mathcal{V}^{\mathrm{x}}$ reaching values near to
22\,Km/s.We also found that the absolute maximum of the response is obtained for
a polarization angle $\alpha = 145^{\circ}$. The decomposition of
$|\mathcal{V}^{\mathrm{a}}|$ in the corresponding $\mathcal{V}^{\mathrm{x}}$,
$\mathcal{V}^{\mathrm{y}}$, and $\mathcal{V}^{\mathrm{z}}$ components is
depicted in Fig. \ref{fig:alt-vxb}. From this figure we can see that for the
energy range from 0.70\,eV to 0.74\,eV all the $x$, $y$, and $z$ components
contribute with almost the same intensity. In the other hand, for the energy
range from 0.88\,eV to 0.95\,eV there is a major contribution coming from the
$\mathcal{V}^{\mathrm{xz}}$ component.

%%%%%%%%%%%%%%%%%%%%%%%%%%% xb [0.6:1.0] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{$\mathcal{V}^{\mathrm{x}}$}
\begin{figure}[tb]
    \centering
    \includegraphics[width=\linewidth]{altplots/alt-magvxb-incang-4545.pdf}
    \includegraphics[width=\linewidth]{altplots/alt-magvyb-incang-4545.pdf}  
    \caption{$|\mathcal{V}^{\mathrm{x}}|$ response for C$_{16}$H$_{8}$-alt structure. The
    maximum response zone is localized for an energy range from 0.90\,eV to
    0.93\,eV. 145$^{\circ}$ and for a polarization angle of the incoming beam from 120$^{\circ}$ to 150$^{\circ}$.}
    \label{fig:alt-magvxbincang}
\end{figure}
\begin{figure}[tb]
    \centering
    \includegraphics[width=\linewidth]{altplots/alt-vab-xb.pdf}
    \caption{Three components of $\mathcal{V}^{\mathrm{x}} $ @ 145$^{\circ}$.}
    \label{fig:alt-vxb}
\end{figure}

% %%%%%%%%%%%%%%%%%%%%%%%%%%% yb [0.6:1.0] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{$\mathcal{V}^{\mathrm{y}}$}
% \begin{figure}[ht]
%     \centering
%     \includegraphics[width=\linewidth]{altplots/alt-magvyb-incang-4545.pdf}
%     \caption{The most intense response for $\mathcal{V}^{\mathrm{y}} $ is for 
%     145$^{\circ}$.}
%     \label{fig:alt-magvybincang1}
% \end{figure}
% \begin{figure}[ht]
%     \centering
%     \includegraphics[width=\linewidth]{altplots/alt-vxx.pdf}
%     \includegraphics[width=\linewidth]{altplots/alt-vxy.pdf}\\
%     \includegraphics[width=\linewidth]{altplots/alt-vxz.pdf}
%     \caption{Cheking angle of incidence for $yb$ components.}
%     \label{fig:alt-ybangcomp}
% \end{figure}
% \begin{figure}[ht]
%     \centering
%     \includegraphics[width=\linewidth]{altplots/alt-vab-yb.pdf}
%     \caption{Three components of $\mathcal{V}^{\mathrm{y}} $ @ 145$^{\circ}$.}
%     \label{fig:alt-vyb1}
% \end{figure}

@@

\bibliographystyle{plain}
\bibliography{article.bib}

>>>>

\documentclass[prb,11pt,tightenlines,twocolumn,aps]{revtex4-1}

% preamble:

\usepackage{amsmath}    % need for subequations
\usepackage{graphicx}   % need for figures
\usepackage{verbatim}   % useful for program listings
\usepackage{color}      % use if color is used in text
\usepackage{subfigure}  % use for side-by-side figures
\usepackage{hyperref}   % use for hypertext links, including those to external
                        % documents and URLs 
\usepackage{blindtext}  % fill text
\usepackage{color}
% \usepackage{showframe}
% \usepackage[inline]{showlabels}

\raggedbottom           % don't add extra vertical space

\begin{document}

\title{Pure Spin Current Injection in Hydrogenated Graphene Structures}
\author{Reinaldo Zapata-Pe\~na\textsuperscript{1},
        Bernardo S. Mendoza\textsuperscript{1},
        Anatoli I. Shkrebtii\textsuperscript{2}}
\affiliation{\textsuperscript{1}Centro de Investigaciones en \'Optica, Le\'on,
Guanajuato 37150, M\'exico}
\affiliation{\textsuperscript{2}University of Ontario, Institute of Technology,
Oshawa, ON, L1H 7L7, Canada}

\date{\today}

\begin{abstract}
\blindtext
\end{abstract}

\maketitle

\section{Introduction}
\blindtext
\begin{figure}[ht!]
    \centering
    \subfigure[\ $xz$ plane view]
    {\includegraphics[width=\linewidth]{figures/altstruc2}}
    \label{fig:alt-struc-xz}
    \\
    \subfigure[\ $xy$ plane view]
    {\includegraphics[width=\linewidth]{figures/altstruc1}}
    \label{fig:alt-struc-xy}
    \caption{Alt structure.}
    \label{fig:alt-struc}
\end{figure}
\begin{figure}[ht!]
    \centering
    \subfigure[\ $xz$ plane view]
    {\includegraphics[width=\linewidth]{figures/upstruc2}}
    \label{fig:up-struc-xz}
    \\
    \subfigure[\ $xy$ plane view]
    {\includegraphics[width=\linewidth]{figures/upstruc1}}
    \label{fig:up-struc-xy}
    \caption{Up structure}
    \label{fig:up-struc}
\end{figure}
\blindtext
\blindtext

\blindtext

@@

\begin{widetext}
\begin{align}
\mathcal{V}^{\mathrm{ab}} (\omega) 
&= \frac{\mu^{\mathrm{abxx}}(\omega)
E^{2}(\omega)\cos^{2}(\alpha) + 
\mu^{\mathrm{abyy}}(\omega)
E^{2}(\omega)\sin^{2}(\alpha) + 
2\mu^{\mathrm{abxy}}(\omega)
E^{2}(\omega)\cos(\alpha)\sin(\alpha)}
{\xi^{\mathrm{xx}}(\omega)
E^{2}(\omega)\cos^{2}(\alpha) + 
\xi^{\mathrm{yy}}(\omega)
E^{2}(\omega)\sin^{2}(\alpha)},
\nonumber \\
&= \frac{\mu^{\mathrm{abxx}}(\omega)\cos^{2}(\alpha) + 
\mu^{\mathrm{abyy}}(\omega)\sin^{2}(\alpha) + 
2\mu^{\mathrm{abxy}}(\omega)\cos(\alpha)\sin(\alpha)}
{\xi^{\mathrm{xx}}(\omega)\cos^{2}(\alpha) + 
\xi^{\mathrm{yy}}(\omega)\sin^{2}(\alpha)}.
\label{eq:vab}
\end{align}
\end{widetext}

@@

We also define $|\mathcal{V}^{\mathrm{a}}|$ as 
\begin{equation}\label{eq:va-mag}
|\mathcal{V}^{\mathrm{a}}| = 
\sqrt {
(\mathcal{V}^{\mathrm{ax}})^{2} +
(\mathcal{V}^{\mathrm{ay}})^{2} +
(\mathcal{V}^{\mathrm{az}})^{2} 
},
\end{equation}
and the corresponding polar and azimuthal angles $\theta$ and $\varphi$ as
\begin{align}
\theta  =& \cos^{-1} \left( \frac{\mathcal{V}^{\mathrm{az}}}
{|\mathcal{V}^{\mathrm{a}}|} \right),
& 0 \leq &\theta \leq \pi, 
\label{eq:polar-ang}
\\
\varphi =& \tan^{-1} \left( \frac{\mathcal{V}^{\mathrm{ay}}}
{\mathcal{V}^{\mathrm{ax}}} \right),
& 0 \leq &\varphi \leq 2\pi.
\label{eq:azimuthal-ang} 
\end{align}

@@

We preset the results for $\mathcal{V}^{\mathrm{ab}}$ for the
C$_{16}$H$_{8}$-alt and C$_{16}$H$_{8}$-up structures being both
noncentrosymmetric semi-infinite carbon systems with 50\% hydrogenation in
different arrangements. The \emph{alt} system has alternating hydrogen atoms on
the upper and bottom sides of the carbon sheet, while the \emph{up} system has H
only on the upper side. We take the hexagonal carbon lattice to be on the $xy$
plane for both structures, and the carbon-hydrogen bonds on the perpendicular
$xz$ plane, as depicted in Figs.
\ref{fig:alt-struc} and \ref{fig:up-struc}.

@@

\begin{table}[tb]
\center
\begin{tabular}{ccccc}\\
\hline
Layer & Atom & \multicolumn{3}{c}{Position [\AA]} \\
\cline{3-5}
No. & type & $x$ & $y$ & $z$  \\
\hline
1 & H &  -0.61516 &  -1.42140 & \ 1.47237 \\
2 & C &  -0.61516 &  -1.73300 & \ 0.39631 \\
3 & C & \ 0.61516 & \ 1.73300 & \ 0.15807 \\
4 & C & \ 0.61516 & \ 0.42201 &  -0.15814 \\
5 & C &  -0.61516 &  -0.37396 &  -0.39632 \\
6 & H &  -0.61516 &  -0.68566 &  -1.47237 \\
\hline
\end{tabular}
\caption{Unit cell of \emph{alt} structure. Layer division, atom types and
positions for the \emph{alt} structure. The structure unit cell was divided in
six layers corresponding each one to atoms in different $z$ positions. The
corresponding layer atom position is depicted in Fig. \ref{fig:alt-struc} with
the corresponding number of layer.}
\label{tab:alt-unitcell}
\end{table}

The structures presented here where divided into layers to analyze the he
layer-by-layer contribution for $\mathcal{V}^{\mathrm{ab}}$ response. The
\emph{alt} structure was divided in six layers corresponding the first one to
the top hydrogen atoms, from the second to the forth to carbon atoms in
different $z$ positions, and the sixth and last one to the bottom hydrogen
atoms. The \emph{up} structure was divided into two layers, the first one
comprised by the top hydrogen atoms and the second by the carbon atoms. The
layer divisions and atom positions for the unit cells are shown in Tables
\ref{tab:alt-unitcell} and \ref{tab:up-unitcell}.

\begin{table}[tb]
\center
\begin{tabular}{ccccc}\\
\hline
Layer & Atom & \multicolumn{3}{c}{Position [\AA]} \\
\cline{3-5}
No. & type & $x$ & $y$ & $z$  \\
\hline
1 & H & -0.61516 & -1.77416 &  0.73196 \\
1 & H &  0.61518 &  0.35514 &  0.73175 \\
2 & C & -0.61516 & -1.77264 & -0.49138 \\
2 & C & -0.61516 & -0.35600 & -0.72316 \\
2 & C &  0.61516 &  0.35763 & -0.49087 \\
\hline
\end{tabular}
\caption{Unit cell of \emph{up} structure. Layer division, atom types and
positions for the \emph{up} structure. The structure unit cell was divided in
two layers corresponding to hydrogen and carbon atoms.The corresponding layer
atom position is depicted in Fig. \ref{fig:up-struc} with the corresponding
number of layer.}
\label{tab:up-unitcell}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% ALT %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{alt} % (fold)
\label{sec:results-alt}
% \subsubsection{$\mathcal{V}^{\mathrm{x}}$}
\begin{figure}[tb]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{alt} structure]
    {\includegraphics[width=\linewidth]{altplots/alt-magvxb-incang-4545.pdf}}
    \label{fig:alt-vx}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{alt} structure]
    {\includegraphics[width=\linewidth]{altplots/alt-magvyb-incang-4545.pdf}}
    \label{fig:alt-vy}
    \caption{$|\mathcal{V}^{\mathrm{x}}|$ response for C$_{16}$H$_{8}$-alt
    structure. The maximum response zone is localized for an energy range from
    0.90\,eV to 0.93\,eV. 145$^{\circ}$ and for a polarization angle of the
    incoming beam from 120$^{\circ}$ to 150$^{\circ}$.}
    \label{fig:alt-vab-mag}
\end{figure}
For the \emph{alt} structure we analyzed the energy range of energy from
0.6\,eV to 1.0\,eV where we found the most intense response for
$\mathcal{V}^{\mathrm{ab}}$ and $|\mathcal{V}^{\mathrm{a}}|$. In Fig. 
\ref{fig:alt-vab-mag} we present the $|\mathcal{V}^{\mathrm{a}}|$ spectra
resulting from evaluate Eq. \eqref{eq:va-mag} using different polarization
angles $\alpha$ in Eq. \eqref{eq:vab} for the C$_{16}$H$_{8}$-alt structure. We
can see that the onset of the response is when the energy of the incoming light
is the same of the gap energy.
%
From this picture we can see that for the zone between the energy range of
0.90\,eV-0.93\,eV and polarization angles between 120$^{\circ}$ and
150$^{\circ}$ is the zone of the absolute maximum response having for both,
$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$. Also there is
another zone of interest for energies from 0.70\,eV to 0.74\,eV where a local
maximum is obtained.
%
From Fig. \ref{fig:alt-vx} we have that $|\mathcal{V}^{\mathrm{x}}|$reaches
values near to 30\,Km/s for the first zone mentioned before and 20\,Km/s for
the second one. 
%
We also found that the absolute maximum of the response is obtained for a
polarization angle $\alpha = 145^{\circ}$. The decomposition of
$|\mathcal{V}^{\mathrm{x}}|$ in the corresponding $\mathcal{V}^{\mathrm{xx}}$,
$\mathcal{V}^{\mathrm{xy}}$, and $\mathcal{V}^{\mathrm{xz}}$ components is
depicted in Fig. \ref{fig:alt-vx-comp} and the decomposition of
$|\mathcal{V}^{\mathrm{y}}|$ in its corresponding $\mathcal{V}^{\mathrm{yx}}$,
$\mathcal{V}^{\mathrm{yy}}$, and $\mathcal{V}^{\mathrm{yz}}$ is shown in Fig.
\ref{fig:alt-vy} for this polarization angle.
%
Making the analysis for $|\mathcal{V}^{\mathrm{x}}|$ we can see that for the
energy range from 0.70\,eV to 0.74\,eV all the $xx$, $xy$, and $xz$ components
contribute with almost the same intensity giving a total spin-velocity near to
30\,Km/s. In the other hand, for the energy range from 0.88\,eV to 0.95\,eV
there is a major contribution coming from the $\mathcal{V}^{\mathrm{xz}}$
component resulting in a spin-velocity near to 20\,Km/s.
%
Also we notice that for the range of 0.70-0.74\,eV all the contributions are
positive while for the range of 0.88-0.95\,eV the $xx$ component remains
positive but the components $xy$ and $xz$ change in direction. This is due to
\textcolor{red}{\large a change in the spin polarization}.
%
Making now the analysis for $|\mathcal{V}^{\mathrm{y}}|$, which is almost two
times more intense than $|\mathcal{V}^{\mathrm{x}}|$, we have that for the
energy range from 0.70\,eV to 0.74\,eV the $yx$ and $yy$ components have a
lesser contribution than $yz$ but for the energy range all three components
have almost the same intensity resulting in a spin-velocity near to 50\,Km/s in
both cases.
%
Now we have that the three components of $|\mathcal{V}^{\mathrm{y}}|$ are
negative for the energy range from 0.65\,eV to 0.95\,eV \textcolor{red}{keeping
the same spin polarization for all this range.}

%%%%%%%%%%%%%%%%%%%%%%%%%%% xb [0.6:1.0] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[tb]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$]
    {\includegraphics[width=\linewidth]{altplots/alt-vab-xb.pdf}}
    \label{fig:alt-vx-comp}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$]
    {\includegraphics[width=\linewidth]{altplots/alt-vab-yb.pdf}}
    \label{fig:alt-vy-comp}
    \caption{Most intense responses of $|\mathcal{V}^{\mathrm{x}}|$ and
    $|\mathcal{V}^{\mathrm{y}}|$ and the corresponding three components for the
    \emph{alt} structure. Both maxima where obtained for a polarization
    angle $\alpha=145^{\circ}$. }
    \label{fig:alt-vab-xy-comp}
\end{figure}

% %%%%%%%%%%%%%%%%%%%%%%%%%%% yb [0.6:1.0] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{$\mathcal{V}^{\mathrm{y}}$}
% \begin{figure}[ht]
%     \centering
%     \includegraphics[width=\linewidth]{altplots/alt-magvyb-incang-4545.pdf}
%     \caption{The most intense response for $\mathcal{V}^{\mathrm{y}} $ is for 
%     145$^{\circ}$.}
%     \label{fig:alt-magvybincang1}
% \end{figure}
% \begin{figure}[ht]
%     \centering
%     \includegraphics[width=\linewidth]{altplots/alt-vab-yb.pdf}
%     \caption{Three components of $\mathcal{V}^{\mathrm{y}} $ @ 145$^{\circ}$.}
%     \label{fig:alt-vyb1}
% \end{figure}

@@

\bibliography{article.bib}
